---
name: Andrés F. Ramírez-Mejía
position: "BSc, MSc, PhD"
address: "Department of Ecology, Zoology and Genetics, Institute of Biology, \\tabularnewline Universidade Federal de Pelotas \\tabularnewline Pelotas (RS), Brasil."
headcolor: "414141"
www: andres-frm.github.io
phone: +55 53 999330101
email: andresfeliper.mejia@gmail.com
github: andres-frm
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
fontsize: 10pt
---



```{r setup, include=FALSE, results='hide', warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pks <- c('vitae', 'tibble', 'tidyverse')

sapply(pks, library, character.only = T)

baretable <- function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL,
                      size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL),
                      longtable = FALSE,
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}

```
# Education

```{r educacion, results='asis'}

tribble(
  ~degree, ~Start, ~Start_month, ~End, ~End_month, ~institution, ~place,
  'B.Sc. Biology', 2008 , 'July ', 2014, 'September ', 'University of Caldas (Colombia)', 'Manizales, Colombia',
  'MSc. Conservation and Use of Biodiversity', 2015 , 'August ', 2017, 'August ', 'Pontifical Javeriana University (Colombia)', 'Bogotá, Colombia',
  'Ph.D. Biological Sciences', 2018 , 'August ', 2023, 'August ', 'National University of Tucumán (Argentina)', 'Tucumán, Argentina',
  'MBA Data science', 2026, 'February ', 2027, 'April', 'Universidade de São Paulo (Brazil)', 'São Paulo, Brazil'
) |> 
  mutate(Date = paste(Start_month, Start, ' -- ', End_month, End, sep = '')) |> 
  detailed_entries(what = degree, 
                   when = Date,
                   where = institution)

```

# Current position

**May 2024 - present**. Postdoctoral researcher with double affiliation: Department of Ecology, Zoology and Genetics, Institute of Biology, Universidade Federal de Pelotas; Department of Zoology & Physiology, University of Wyoming. *Projects*: [Army Ant Followers Project](https://www.tarwaterlab.com/copy-of-panama-plumas-project), and [Hawaii-VINE  Project.](https://www.tarwaterlab.com/hawaii-vine-project)

# Technical skills
-   Experimental design and data collection.
-   Causal inference (Pearl framework).
-   Data analysis: frequentist and Bayesian statistics (lm, glm, glmm, hierarchical models), Gaussian process models, time series analysis, structural equation modeling, Bayesian networks, network analysis, and simulation studies.
-   Machine learning: regression trees, random forests, basic deep learning.
-   Programming languages: R (advanced), Python (intermediate) and Stan (intermediate).
-   Spatial analysis tools: Google Earth Engine (basic), ArcGis (basic) and R packages: *terra*, *raster*, and *sf* (basic).
-   Other tools: Git and GitHub for version control. RMarkdown and Quarto for report generation.

--------------------------------

## Published articles

-   Harold Pulido-Guarín, Ana Carolina Monmany-Garzia, Alejandra Carla Scannapieco, **Ramírez-Mejía A. F.**, Martín Geria, Alberto Galindo-Cardona. **(2026)**. Three methods for measuring the Earth’s magnetic field intensity in Apis mellifera (Hymenoptera: Apidae) drone congregation areas, Environmental Entomology, Volume 55, Issue 3, June 2026, nvag056, https://doi.org/10.1093/ee/nvag056
-   **Ramírez-Mejía, A. F.**, Sánchez, F., Urbina-Cardona, J. N., & Ladino, N. **(2026)**. Functional divergence drives the prevalence of low-abundance species in bat assemblages. Functional Ecology, 40(6), 1587-1602. <https://doi.org/10.1111/1365-2435.70333>
-   Wolter, J. H., Vissoto, M., **Ramírez‐Mejía, A. F**., Vizentin‐Bugoni, J., & Dias, R. A. **(2026)**. Intrinsic and extrinsic drivers shape frugivore functional diversity within a tree population. Ecosphere, 17(2). https://doi.org/10.1002/ecs2.70453
-   Gómez-Murillo, L., Vizentin-Bugoni, J., **Ramírez-Mejía, A. F.**, & Tarwater, C. E. **(2026)**. Rainfall alters network structure, while fragmentation results in the breakdown of a mixed-species group of birds. Oecologia, 208(2), 34. https://doi.org/10.1007/s00442-026-05869-7.
-   Chacoff, N., Monmany-Garzia, A. C., **Ramírez-Mejía, A. F.**, Castillo, S., Aragón, R. Hacia una agricultura sustentable: ¿Por qué nos importa la biodiversidad? In: Brown, A., & Sánchez, E. Argentina Sustentable: El Norte Grande. 1. ed. Yerba Buena, Argentina: Ediciones Del Subtrópico, 2025. p. 472-476. **ISBN 978-631-90041-4-4**.
-   **Ramírez-Mejía A. F.**, Chacoff N., Cavigliasso P., Blendinger P. **(2024)**. How much is enough? Optimizing beehive stocking densities to maximize the production of a pollinator-dependent crop. *Ecological modelling*, vol 498, article number: <https://doi.org/10.1016/j.ecolmodel.2024.110891>.
-   Monasterologo, M, **Ramírez-Mejía A. F.**, et al. **(2024)**. Animal pollination contributes to more than half of Citrus spp. production despite the species and cultivar. *Scientific reports*, vol 14, Article number: 22309.  <https://www.nature.com/articles/s41598-024-73591-6>.
-   Fontanarrosa G., Zarbá L., ... **Ramírez-Mejía A. F.** ... Piquer-Rodríguez M. **(2024)**. Over twenty years of publications in Ecology: Over-contribution of Women reveals a new dimension of gender bias. *PLOS ONE*.  <https://doi.org/10.1371/journal.pone.0307813>
-   **Ramírez-Mejía A F**, Chacoff N, Lomáscolo S, Woodcock B, Schmucki R & Blendinger P. **(2024)**. Optimal pollination thresholds to maximize blueberry production. *Agriculture Ecosystems and Environment* <https://doi.org/10.1016/j.agee.2024.108903>
-   **Ramírez-Mejía A F**, Blendinger P, Woodcock B, Schmucki R, Escobar L, Morton R, Vieli L, Nunes-Silva P, Lomáscolo S, Morales C, Murúa M, Agostini K, & Chacoff N. **(2023)**. Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries. *Journal of Applied Ecology*. DOI: <https://doi.org/10.1111/1365-2664.14553>
-   Nunes-Silva Patrícia, **Ramírez-Mejía Andrés F.**, Blochtein B, Ramos J, Agostini K, Vieli L, Santanna M, Raguse-Quadros M, Maureen M., Chacoff N P, Cavigliasso P, Blendinger P G., Domingos S. **(2023)**. Blueberry: pollination and production in South America. ISBN: 978-65-00-65347-2. DOI: <https://doi.org/10.5281/zenodo.7770381>.
-   **Ramírez-Mejía A F**, Lomáscolo S & Blendinger P. **(2023)** Hummingbirds, honeybees, and wild insect pollinators affect yield and berry quality of blueberries depending on cultivar and farm's spatial context. *Agriculture Ecosystems and Environment*. DOI: <https://doi.org/10.1016/j.agee.2022.108229>
-   Blendinger P G, Rojas T N, **Ramírez-Mejía A F**, Bender I M A, Lomáscolo S, Magro J, Núñez Montellano M G, Ruggera R A, Valoy M & Ordano M. **(2022)** [*Nutrient balance and energy-acquisition effectiveness: do birds adjust their fruit diet to achieve intake targets?*](https://doi.org/10.1111/1365-2435.14164) *Functional Ecology*. DOI: doi.org/10.1111/1365-2435.14164
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2022)**. [*The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat*](doi:10.1017/S026646742100047X). *Journal of Tropical Ecology*. 38(1), 31-38. DOI: <https://10.1017/S026646742100047X>
-   **Ramírez-Mejía A F**, Echeverry-Galvis M A, & Sánchez F. **(2021)**. [*Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation*](https://doi.org/10.1676/19-54). *Wilson Journal of Ornithology*. 132(3): 721-729. DOI: doi.org/10.1676/19-54
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2020)** [*Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis*](https://doi.org/10.1111/btp.12816). *Biotropica*. 52(6): 1168-1182. DOI: <https://doi.org/10.1111/btp.12816>.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2016)**. [*Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia*](http://doi.org/10.4404/hystrix-27.2-11319). *Hystrix, the Italian Journal of Mammalogy*, 27(2): 104-110. DOI: <https://doi.org/10.4404/hystrix-27.2-11319>.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2015)**. [*Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin*](http://dx.doi.org/10.15560/11.2.1582). *Check List*, 11(2):1-6, Article 1582. DOI: <https://dx.doi.org/10.15560/11.2.1582>.


## Under review

-   **Ramírez-Mejía A. F.**, Mary De Aquino, Michael Castaño Díaz, Juliana Hinz Wolter, Henry S. Pollock, J. Patrick Kelley, Jeferson Vizentin-Bugoni & Corey E. Tarwater. Biotic and abiotic factors directly and indirectly impact the structure of non-trophic networks across a rainfall gradient. *Journal: Ecology*. **Role: first author**

-   Elizabeth J. Howard, **Andrés F. Ramírez-Mejía**, Michael Castaño, Mary De Aquino, Henry S. Pollock, Jefferson Vizentin-Bugoni, and Corey E. Tarwater. Testing long standing assumptions about army ant swarms: how profitability and dominance alter space use in birds. *Journal: Behavioral Ecology* .**Role: coauthor, data analysis**

-  Jordan, Kimberley; **Ramírez-Mejía, Andrés F**.; Wilcox, Rebecca C.; Brawn, Jeffrey ; Alfonso, Camilo; Tarwater, Corey. Testing the space-for-time assumption and the hygric niche hypothesis using precipitation effects on avian body condition. *Journal: Proceedings of the Royal Society B: Biological Sciences*. **Role: coauthor, data analysis**

-   **Andrés F. Ramírez-Mejía**, Corey E. Tarwater, J. Patrick Kelley, Jinelle H. Sperry, Jeffrey T. Foster, Donald R. Drake, and Jeferson Vizentin-Bugoni. Temporal dynamics of seed-dispersal networks: Disentangling the role of direct biotic and abiotic factors and bottom-up processes. *Journal: Ecology*. **Role: first author**

-   Mary De Aquino1, Henry S. Pollock, J. Patrick Kelley, **Andrés F. Ramírez-Mejía**, Michael Castaño Díaz1, Jeferson Vizentin-Bugoni  & Corey E. Tarwater. Species’ roles, specialization, and the factors that influence roles in mixed-species animal groups. **Journal of Animal Ecology**. **Role: review**


## Code and online datasets

-   **Ramírez-Mejía, Andrés F**. (2026). Intrinsic and extrinsic drivers modulate the functional diversity of frugivorous birds interacting with individual trees within a population [code]. **Ecosphere**. Zenodo. <https://doi.org/10.5281/zenodo.17334865>

-   **Ramírez-Mejía, Andrés F**. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [code]. **Journal of Applied Ecology**. Zenodo. <https://doi.org/10.5281/zenodo.10070657>

-   **Ramírez-Mejía, Andrés F**. et al. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [Dataset]. **Journal of Applied Ecology**. Dryad. <https://doi.org/10.5061/dryad.bg79cnphc>

-   **Ramírez-Mejía, A F**.; Urbina-Cardona, J N; Sánchez, F (2020). Data from: Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis [Dataset]. **Biotropica**. Dryad. <https://doi.org/10.5061/dryad.sn02v6x1p>


