---
name: Andrés F. Ramírez-Mejía
profilepic: andresSURPASS2.jpg
position: "PhD fellow at CONICET"
address: "Institute of Regional Ecology UNT-CONICET"
headcolor: 008000
phone: +54 3816627944
email: "andresfeliper.mejia@gmail.com"
twitter: felipe_arm_
github: andres-frm
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
aboutme: "I'm a biologist interested in using landscape and functional ecology and plant-animal interactions to study how spatial patterns modulate biological responses of mammals and pollinators. I'm very passionate about nature, literature, data science, and R programming."
 
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r educacion}
library(tibble)
tribble(
  ~ `Título`, ~ Año, ~ Institución, ~ Lugar, 
  "PhD. Biological science", "2018-Present", "Universidad Nacional de Tucumán", "Tucumán, Argentina",
  "MSc. Conservation and Use of Biodiversity", "2015-2017", "Pontificia Universidad Javeriana", "Bogotá, Colombia", 
  "BSc. Biologist", "2008-2014", "Universidad de Caldas", "Manizales, Colombia", 
) %>% 
  detailed_entries(what = `Título`, 
                   when = `Año`,
                   with = Institución,
                   where = Lugar)

```

# Awards and distinctions

* **2017** Academic merit award during studies of master degree, at the Pontificia Universidad Javeriana. Bogotá, Colombia.

* **2017** Graduated with honors CUM LAUDE. Master in Conservation and Use of Biodiversity at the Pontificia Universidad Javeriana. Pontificia Universidad Javeriana. Bogotá, Colombia

* **2017** Master degree thesis with honorary mention. Master in Conservation and Use of Biodiversity at the Pontificia Universidad Javeriana. Bogotá, Colombia.

* **2017** Doctoral fellowship granted by National Scientific and Technical Research Council - Argentina (CONICET). Resolution N° 4122. Thesis: Interacciones planta-animal en cultivos de arándanos (*Vaccinium corymbosum*, Ericaceae) y efectos recíprocos con el bosque nativo de Yungas. 


# Research grants

```{r subsidios}

tribble(
  ~beca, ~institucion, ~proyecto, ~año, ~monto, ~lugar, 
  "François Vuilleumier Fund for Research on Neotropical Birds", "Neotropical Ornithological Society", "Servicios ecosistémicos provistos por picaflores (Trochilidae): la polinización del arándano en el noroeste de Argentina", "2018", "$1000 US", "EEUU",
  "Beca Aves Argentinas, de Apoyo a la Ornitología Argentina", "Aves Argentinas - Sociedad Ornitológica de la Plata", "Servicios ecosistémicos provistos por picaflores (Trochilidae): la polinización del arándano en el noroeste de Argentina", "2020", "$50000 ARS ($640 US)", "Argentina"
) %>% 
  detailed_entries(with = beca,
                   what = glue::glue("Awarded in {año} by {institucion}"),
                   where = lugar,
                   when = monto,
                   why = proyecto
                   )


```




# Publications and oral presentations

## **Published articles**

1. **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. [The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat](doi:10.1017/S026646742100047X). *Journal of Tropical Ecology*. 38(1), 31-38. DOI: doi:10.1017/S026646742100047X

2. **Ramírez-Mejía A F**, Echeverry-Galvis M A, & Sánchez F. (2021). [Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation](https://doi.org/10.1676/19-54) . *Wilson Journal of Ornithology*. 132(3): 721-729. DOI: doi.org/10.1676/19-54

3. **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. (2020) [Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis](https://doi.org/10.1111/btp.12816). *Biotropica*. 52(6): 1168-1182. DOI: doi.org/10.1111/btp.12816.

4. **Ramírez-Mejía A F**, & Sánchez F. (2016). [Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia](http://doi.org/10.4404/hystrix-27.2-11319). *Hystrix, the Italian Journal of Mammalogy*, 27(2): 104-110. DOI: doi.org/10.4404/hystrix-27.2-11319. 

5. **Ramírez-Mejía A F**, & Sánchez F. (2015). [Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin](http://dx.doi.org/10.15560/11.2.1582). *Check List*, 11(2):1-6, Article 1582. DOI: dx.doi.org/10.15560/11.2.1582.


## **Under review**

1. **Ramírez-Mejía A F**, Lomáscolo S & Blendinger P. Hummingbirds, honeybees, and wild insect pollinators enhance fruit quality of blueberries depending on variety and farm’s spatial context. *Agriculture Ecosystems and Environment*

2. Blendinger P G, Rojas T N, **Ramírez-Mejía A F**, Bender I M A, Lomáscolo S, Magro J, Núñez Montellano M G, Ruggera R A, Valoy M & Ordano M. Nutrient balance and energy-acquisition  effectiveness: do birds adjust their fruit diet to achieve intake targets? *Functional Ecology*

## **In preparation**
1. **Ramírez-Mejía A F**, Dos Santos D A, Chacoff N, Lomáscolo S & Blendinger P. Integrating fuzzy logic and pollination ecology for better crop production: a study case assessing pollination service in blueberry crops.

2. **Ramírez-Mejía A F**, Lomáscolo S, & Blendinger P. Individual and population effectiveness of hummingbirds, wild and managed insect pollinating blueberry crops.

3. **Ramírez-Mejía A F**, Lomáscolo S, Chacoff N, Blendinger P. The step by step of pollination service process in blueberry crops.


## **Theses**

```{r, eval=FALSE}

tribble(
  ~año, ~titulo, ~tesis,
  2014, "BSc", "Actividad, uso de hábitat y riqueza de mamíferos en un bosque nativo y uno reforestado con eucalipto en los Andes colombianos",
  2017, "MSc", "Diversidad funcional, taxonómica y dispersión de semillas por murciélagos filostómidos en un paisaje antropizado: un análisis multiescala",
  2018, "PhD", "Interacciones planta-animal en cultivos y efectos recíprocos con el bosque nativo de Yungas"
) %>% vitae::brief_entries(with = año,
                           what = tesis,
                           when = glue::glue("{titulo}"))
```

**PhD**. 2018 - Present. Plant-animal interactions in crops and reciprocal effects with the Yungas forest. Thesis advisors: Pedro G. Blendinger, PhD; independent research CONICET, assistant professor UNT. Silvia Lomáscolo, PhD; assistant researcher CONICET.

**MSc**. 2017. Functional and taxonomic diversity, and seed dispersion by phyllostomid bats in an anthropogenic landscape: a scale-dependent analysis. Thesis advisors: Francisco Sánchez, PhD; Universidad de los Llanos, Colombia. J. Nicolás Urbina-Cardona, PhD; Pontificia Universidad Javeriana, Colombia.

**BSc**. 2014. Activity pattern, habitat use, and mammals richness in native and reforested forests at the Colombian Andes. Thesis advisor: Francisco Sánchez, PhD; Universidad Militar Nueva Granada, Cundinamarca, Colombia.



## **Oral Presentations**

```{r P_orales, eval=FALSE}
tribble(
  ~año, ~evento, ~presentacion, ~lugar,
  2014, "II Simposio colombiano de pequeños carnívoros. IV Congreso colombiano de zoología", "Activity and habitat use of soil forage mammals in an Andean forest and a Eucalyptus reforestation", "Cartagena, Colombia",
  2014, "III Simposio regional de biología.", "Species richness, use and traditional knowledge of mammals in the National Natural Park Los Nevados", "Armenia, Colombia"
) %>% 
  detailed_entries(with = evento,
                   what = presentacion,
                   when = año,
                   where = lugar)
```

**2021**. *Blueberry pollination at the NOA, are wild species important?*. Tucumán, Argentina.

**2014**. *Activity and habitat use of soil forage mammals in an Andean forest and a Eucalyptus reforestation*. II Symposium of small carnivores. IV Colombian congres fo zoology. Cartagena, Colombia.

**2014**. *Species richness, use and traditional knowledge of mammals in the National Natural Park Los Nevados*. III Symposium of regional biology. Armenia, Colombia.

# Teaching

```{r docente}
tribble(
  ~curso, ~institucion, ~nivel, ~lugar, ~año, ~comentario,
  "Introduction to R programming", "Universidad Nacional de Tucumán, Facultad de Ciencias Naturales e Instituto Miguel Lillo", "Undergraduate", "Tucumán, Argentina", 2019, "Biological Science",
  "Data Clinic", "Universidad Nacional de Tucumán, Facultad de Ciencias Naturales e Instituto Miguel Lillo", "PhD", "Tucumán, Argentina", 2021, "Biological Science, Agronomy and Biotechnology"
) %>% 
  detailed_entries(
    with = curso,
    what = institucion,
    where = lugar,
    when = año,
    why = glue::glue("Offered to {comentario} students. Level: {nivel}.")
  )

```

# Graduate courses

```{r cursos_posgrado}

tribble(
  ~curso, ~institucion, ~lugar, ~año, ~duracion, ~nota,
  "Data science with Python", "Universidad Nacional de la Patagonia Austral", "Argentina (online)", 2022, "40h", "10/10",
  "Models and data in ecology", "Universidad Nacional de Comahue", "Bariloche, Argenttina (online)", 2021, "40h", "9/10",
  "Statistical tools for addressing gender metrics: a look from graph and systems theory", "Universidad Nacional de Tucumán", "Tucumán, Argentina", 2021, "40h", "100/100",
  "Ecological networks", "Universidad de São Paulo", "São Paulo, Brasil", 2020, "60h", "Excellent",
  "Pollination Ecology", "Universidad Nacional del Comahue", "Bariloche, Argentina", 2019, "60h", "100/100",
  "13° International Pollination Course", "Brazilian Network of Plant-Pollination Research (REBIPP)", "Minas Gerais, Brasil", 2019, "98h", "100/100",
  "Advanced statistical methods in ecology and evolution", "Facultad de Ciencias, Universidad de la República Uruguay", "Maldonado, Uruguay", 2019, "60h", "100/100",
  "Advanced statistical models using programming language R", "Universidad Nacional de Córdoba", "Córdoba Argentina", 2018, "40h", "100/100"
) %>% 
  detailed_entries(with = curso,
                   what = institucion,
                   where = lugar,
                   when = año,
                   why = glue::glue("Duration: {duracion}. Grade: {nota}"))

```


# Internships

```{r pasantia}
tribble(
  ~pasantia, ~institucion, ~lugar, ~año, ~duracion,
  "Laboratory of Palynology", "Facultad de Ciencias Naturales e instituto Migue Lillo, Universidad Nacional de Tucumán", "Tucumán, Argentina", 2018, "20h"
  
) %>% detailed_entries(with = pasantia,
                       what = institucion,
                       when = año,
                       where = lugar,
                       why = glue::glue("Duration: {duracion}"))

```



# Member of research groups (Colombia)

```{r grupoI}

tribble(
  ~grupo, ~clasificacion, ~institucion, ~vinculacion, ~fechaI, ~fechaF, ~lugar,
  "InQuiBio (Grupo integrado de investigaciones en química y biología)", "A1", "Universidad Militar Nueva granada", "Integrante", "Jan 2013", "Dec 2015", "Bogotá, Colombia",
  "Ecotonos (Grupo de ecología, conservación, taxonomía y sistemática)", "C", "Universidad de los LLanos", "Integrante", "Jan 2017", "Present", "Villavicencio, Colombia"
) %>% 
  detailed_entries(with = grupo,
                   what = institucion,
                   why = glue::glue("Classification: {clasificacion}."),
                   where = lugar,
                   when = glue::glue("{fechaI}-{fechaF}"))

```

# Languages
* Spanish: mother language.
* English: written (good), reading (good), spoken (acceptable).

# Driver license
* No. 1053795821. Validity: 03-06-2028. Category: B1. Issued: Colombia (03-06-2018)