---
name: Andrés F. Ramírez-Mejía
position: "BSc, MSc, PhD"
address: "Institute of Regional Ecology, UNT-CONICET \\tabularnewline Yerba Buena, Argentina."
headcolor: "414141"
www: andres-frm.github.io
phone: +54 9 3816627944
email: andresfeliper.mejia@gmail.com
github: andres-frm
output: vitae::hyndman
fontsize: 10pt
---

```{r setup, include=FALSE, results='hide', warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pks <- c('vitae', 'tibble', 'tidyverse')

sapply(pks, library, character.only = T)

baretable <- function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL,
                      size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL),
                      longtable = FALSE,
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}

```


# Education

```{r educacion, results='asis'}

tribble(
  ~degree, ~Start, ~Start_month, ~End, ~End_month, ~institution, ~place,
  'B.Sc. Biology', 2008 , 'July ', 2014, 'Sept ', 'University of Caldas (Colombia)', 'Manizales, Colombia',
  'MSc. Conservation and Use of Biodiversity', 2015 , 'Aug ', 2017, 'Aug ', 'Pontifical Javeriana University (Colombia)', 'Bogotá, Colombia',
  'Ph.D. Biological Sciences', 2018 , 'Aug ', 2023, 'Aug ', 'National University of Tucumán (Argentina)', 'Tucumán, Argentina'
) |> 
  mutate(Date = paste(Start_month, Start, ' -- ', End_month, End, sep = '')) |> 
  arrange(desc(Start)) |> 
  select(degree, institution, Date) |> 
  baretable()

```

# Current position

```{r, results='asis'}

tribble(
  ~year1, ~month1, ~year2, ~month2,  ~position,
  2023, 'Aug', 2026, 'Aug', 'Postdoctoral researcher at the Institute of Regional Ecology, UNT-CONICET.'
) |> 
  mutate(date = paste(month1, year1, '-', 'Present')) |> 
  select(date, position) |> 
  baretable()

```
-   **Project:** *Control systems for pollination service management in blueberry crops.* 

# Research interests

-   Functional diversity and ecosystem services.
-   Community ecology.
-   Species interactions.
-   Pollinators and mammal ecology.
-   Landscape ecology.
-   Statistics, programming languages and data science.

Currently, I am working on combining different modeling approaches and field experiments to understand how spatial patterns affect biodiversity and ecosystem services in agricultural landscapes of Northern Argentina.

# Technical skills
-   Experimental design and data collection.
-   Data analysis: frequentist and Bayesian statistics (lm, glm, glmm, hierarchical models), structural equation modeling, network analysis, fuzzy logic and agent-based modeling.
-   Statistical programming: R (advanced), Python (basic) and Stan (basic).
-   Spatial analysis tools: Google Earth Engine (basic) and ArcGis (basic).
-   Other tools: Git, RMarkdown and Quarto.

--------------------------------


# List of publications

-   **Ramírez-Mejía A F**, Chacoff N, Lomáscolo S, Woodcock B, Schmucki R & Blendinger P. **(2024)**. Optimal pollination thresholds to maximize blueberry production. *Agriculture Ecosystems and Environment* <https://doi.org/10.1016/j.agee.2024.108903>
-   **Ramírez-Mejía A F**, Blendinger P, Woodcock B, Schmucki R, Escobar L, Morton R, Vieli L, Nunes-Silva P, Lomáscolo S, Morales C, Murúa M, Agostini K, & Chacoff N. **2023**. *Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries*. *Journal of Applied Ecology*. DOI: <https://doi.org/10.1111/1365-2664.14553>
-   Nunes-Silva Patrícia, **Ramírez-Mejía Andrés F.**, Blochtein B, Ramos J, Agostini K, Vieli L, Santanna M, Raguse-Quadros M, Maureen M., Chacoff N P, Cavigliasso P, Blendinger P G., Domingos S. **(2023)**. *Blueberry: pollination and production in South America*. ISBN: 978-65-00-65347-2. DOI: <https://doi.org/10.5281/zenodo.7770381>.
-   **Ramírez-Mejía A F**, Lomáscolo S & Blendinger P. **(2023)** *Hummingbirds, honeybees, and wild insect pollinators affect yield and berry quality of blueberries depending on cultivar and farm's spatial context*. *Agriculture Ecosystems and Environment*. DOI: <https://doi.org/10.1016/j.agee.2022.108229>
-   Blendinger P G, Rojas T N, **Ramírez-Mejía A F**, Bender I M A, Lomáscolo S, Magro J, Núñez Montellano M G, Ruggera R A, Valoy M & Ordano M. **(2022)** [*Nutrient balance and energy-acquisition effectiveness: do birds adjust their fruit diet to achieve intake targets?*](https://doi.org/10.1111/1365-2435.14164) *Functional Ecology*. DOI: doi.org/10.1111/1365-2435.14164
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2022)**. [*The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat*](doi:10.1017/S026646742100047X). *Journal of Tropical Ecology*. 38(1), 31-38. DOI: <doi:10.1017/S026646742100047X>
-   **Ramírez-Mejía A F**, Echeverry-Galvis M A, & Sánchez F. **(2021)**. [*Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation*](https://doi.org/10.1676/19-54). *Wilson Journal of Ornithology*. 132(3): 721-729. DOI: doi.org/10.1676/19-54
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2020)** [*Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis*](https://doi.org/10.1111/btp.12816). *Biotropica*. 52(6): 1168-1182. DOI: doi.org/10.1111/btp.12816.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2016)**. [*Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia*](http://doi.org/10.4404/hystrix-27.2-11319). *Hystrix, the Italian Journal of Mammalogy*, 27(2): 104-110. DOI: doi.org/10.4404/hystrix-27.2-11319.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2015)**. [*Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin*](http://dx.doi.org/10.15560/11.2.1582). *Check List*, 11(2):1-6, Article 1582. DOI: dx.doi.org/10.15560/11.2.1582.


### Articles in preparation

-   **Ramírez-Mejía A F**, Lomáscolo S, & Blendinger P. *Individual and population effectiveness of hummingbirds, wild and managed insects pollinating blueberry crops*.

## Code and online datasets

-   **Ramírez-Mejía, Andrés F**. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [code]. **Journal of Applied Ecology**. Zenodo. <https://doi.org/10.5281/zenodo.10070657>

-   **Ramírez-Mejía, Andrés F**. et al. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [Dataset]. **Journal of Applied Ecology**. Dryad. <https://doi.org/10.5061/dryad.bg79cnphc>

-   **Ramírez-Mejía, A F**.; Urbina-Cardona, J N; Sánchez, F (2020). Data from: Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis [Dataset]. **Biotropica**. Dryad. <https://doi.org/10.5061/dryad.sn02v6x1p>

-----------------------------

# Fellowships 

-   **2023**. Postdoctoral fellowship financed by CONICET, Argentina. RESOL‐2023‐1026‐APN‐DIR#CONICET.

-   **2017**. PhD fellowship financed by CONICET, Argentina. N° 4122.

# Research grants

```{r results='asis'}

tribble(
  ~year, ~proyect, ~funding, ~grant,
  2020, 'Ecosystem services provided by hummingbirds (Trochilidae)','Research grant Aves Argentinas (ARG)', 640,
  2018, 'Ecosystem services provided by hummingbirds (Trochilidae)','Neotropical Ornithological Society (USA)', 1000,
) |> 
  mutate(US = paste(paste('\\$', grant, sep = ''), 'US')) |> 
  select(proyect, funding, year, US) |> 
  baretable()

```


# Distinctions

```{r, results='asis'}

tribble(
  ~year, ~award,
  2017, 'Academic merit award. During MSc degree at Pontifical Javeriana University',
  2017, 'Graduated with honors CUM LAUDE. During MSc degree at Pontifical Javeriana University',
  2017, 'MSc thesis with honorary mention. During MSc degree at Pontifical Javeriana University'
) |> 
  select(award, year) |> 
  baretable()

```


# Teaching experience

```{r docente, results='asis'}
tribble(
  ~curse, ~institution, ~level, ~year,
  "Data Clinic", "National University of Tucumán", "graduate",  2021, 
  "Introduction to R programming", "National University of Tucumán", "undergraduate", 2019
) |> 
  mutate(
    curse_level = paste(curse, paste('(Level: ', level, ')', sep = ''), sep = ' ')
  ) |> 
  select(curse_level, institution, year) |> 
  baretable()

```

# Graduate courses

```{r cursos_posgrado, results='asis'}

tribble(
  ~year, ~course, ~institution, ~hours, ~country,
  2023, 'Google Earth Engine - Integral', 'REDES Center (CONICET)', 60, 'Argentina',
  2022, 'Introduction to Bayesian statistics methods in ecology', 'University of Buenos Aires', 45, 'Argentina',
  2022, 'Ecosystem services: concepts, tools and perspectives', 'National University of Cuyo', 45, 'Argentina',
  2022, 'Data science with Python', 'National University of Southern Patagonia', 40, 'Argentina',
  2021, 'Models and data in ecology', 'National University of Comahue', 40, 'Argentina',
  2021, 'Statistical tools for addressing gender metrics', 'National University of Tucumán', 40, 'Argentina',
  2020, 'Ecological networks', 'University of São Paulo', 60, 'Brazil',
  2019, 'Pollination Ecology', 'National University of Comahue', 60, 'Argentina',
  2019, '13° International Pollination Course', 'Federal University of Jequitinhonha Valleys', 98, 'Brazil',
  2019, 'Advanced statistical methods in ecology and evolution', 'University of the Uruguay Republic', 60, 'Uruguay',
  2018, 'Advanced statistical models using programming language R', 'National University of Córdoba', 40, 'Argentina'
) |> 
  mutate(h = paste(hours, 'h', sep = '')) |> 
  select(course, institution, h, country, year) |> 
  baretable()
  
```


# Languages

-   Spanish (mother language).
-   English (reading: excellent, speaking: good).

----------------------------------

# References list

\
**Natacha P. Chacoff** \
Independent researcher CONICET, Argentina \
Assistant professor, National University of Tucumán (Argentina) \
e-mail: nchacoff@gmail.com \
[Google scholar profile](https://scholar.google.com.ar/citations?user=rxJBqGcAAAAJ&hl=en) \


\
**J. Nicolás Urbina-Cardona** \
Assistant professor, Pontifical Javeriana University (Colombia) \
e-mail: urbina-j@javeriana.edu.co \
[Google scholar profile](https://scholar.google.ca/citations?hl=en&user=uMBjaFgAAAAJ) \


\
**Ben A. Woodcock** \
Researcher, UK Centre for Ecology & Hydrology (Wallingford, UK) \
e-mail: bawood@ceh.ac.uk \
[Google scholar profile](https://scholar.google.ca/citations?user=u4JXDGEAAAAJ&hl=en) \