---
name: Andrés F. Ramírez-Mejía
profilepic: andresSURPASS2.jpg
position: "Postdoctoral researcher at CONICET"
address: Institute of Regional Ecology UNT-CONICET
headcolor: "414141"
phone: +54 9 3816627944
email: andresfeliper.mejia@gmail.com
twitter: felipe_arm_
github: andres-frm
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
aboutme: I am currently investigating the patterns and mechanisms that determine the contribution of pollinators to blueberry production in northwestern Argentina. I seek to understand the effects on different productive metrics of the crop, detect optimal pollination thresholds, and evaluate the role played by the spatial context in regulating the pollination service. I am passionate about nature, literature, data analysis, and R programming.
 
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r educacion}
library(tibble)
tribble(
  ~ `Título`, ~ Año, ~ Institución, ~ Lugar, 
  "PhD. Biological science", "2018-2023", "Universidad Nacional de Tucumán", "Tucumán, Argentina",
  "MSc. Conservation and Use of Biodiversity", "2015-2017", "Pontificia Universidad Javeriana", "Bogotá, Colombia", 
  "BSc. Biologist", "2008-2014", "Universidad de Caldas", "Manizales, Colombia", 
) %>% 
  detailed_entries(what = `Título`, 
                   when = `Año`,
                   with = Institución,
                   where = Lugar)

```

# Awards and distinctions

* **2023** Postdoctoral fellowship granted by National Scientific and Technical Research Council - Argentina (CONICET). Resolution. Resolution: RESOL-2023-1026-APN-DIR#CONICET

* **2017** Doctoral fellowship granted by National Scientific and Technical Research Council - Argentina (CONICET). Resolution N° 4122. Thesis: Plant-animal interactions in blueberry crops (*Vaccinium corymbosum*, Ericaceae) and reciprocal effects with the Yungas native forest. 

* **2017** Academic merit award during studies of master degree, at the Pontificia Universidad Javeriana. Bogotá, Colombia.

* **2017** Graduated with honors CUM LAUDE. Master in Conservation and Use of Biodiversity at the Pontificia Universidad Javeriana. Pontificia Universidad Javeriana. Bogotá, Colombia

* **2017** Master degree thesis with honorary mention. Master in Conservation and Use of Biodiversity at the Pontificia Universidad Javeriana. Bogotá, Colombia.



# Research grants

```{r subsidios}

tribble(
  ~beca, ~institucion, ~proyecto, ~año, ~monto, ~lugar, 
  "Research grant Aves Argentinas to support Argentinian ornithology", "Ornithological Society of La Plata", "Ecosystem services provided by hummingbirds (Trochilidae): the pollination of blueberry in the Argentinian northeastern", "2020", "$50000 ARS ($640 US)", "Argentina",
  "François Vuilleumier Fund for Research on Neotropical Birds", "Neotropical Ornithological Society", "Ecosystem services provided by hummingbirds (Trochilidae): the pollination of blueberry in the Argentinian northeastern", "2018", "$1000 US", "EEUU"
) %>% 
  detailed_entries(with = beca,
                   what = glue::glue("Awarded in {año} by {institucion}"),
                   where = lugar,
                   when = monto,
                   why = proyecto
                   )


```




# Publications and oral presentations

## **Published articles**

1. **Ramírez-Mejía A F**, Lomáscolo S & Blendinger P. (2023) [Hummingbirds, honeybees, and wild insect pollinators affect yield and berry quality of blueberries depending on cultivar and farm’s spatial context](https://doi.org/10.1016/j.agee.2022.108229). *Agriculture Ecosystems and Environment*. DOI: https://doi.org/10.1016/j.agee.2022.108229

2. Blendinger P G, Rojas T N, **Ramírez-Mejía A F**, Bender I M A, Lomáscolo S, Magro J, Núñez Montellano M G, Ruggera R A, Valoy M & Ordano M. (2022) [Nutrient balance and energy-acquisition  effectiveness: do birds adjust their fruit diet to achieve intake targets?](https://doi.org/10.1111/1365-2435.14164) *Functional Ecology*. DOI: doi.org/10.1111/1365-2435.14164

3. **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. (2022). [The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat](doi:10.1017/S026646742100047X). *Journal of Tropical Ecology*. 38(1), 31-38. DOI: doi:10.1017/S026646742100047X

4. **Ramírez-Mejía A F**, Echeverry-Galvis M A, & Sánchez F. (2021). [Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation](https://doi.org/10.1676/19-54) . *Wilson Journal of Ornithology*. 132(3): 721-729. DOI: doi.org/10.1676/19-54

5. **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. (2020) [Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis](https://doi.org/10.1111/btp.12816). *Biotropica*. 52(6): 1168-1182. DOI: doi.org/10.1111/btp.12816.

6. **Ramírez-Mejía A F**, & Sánchez F. (2016). [Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia](http://doi.org/10.4404/hystrix-27.2-11319). *Hystrix, the Italian Journal of Mammalogy*, 27(2): 104-110. DOI: doi.org/10.4404/hystrix-27.2-11319. 

7. **Ramírez-Mejía A F**, & Sánchez F. (2015). [Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin](http://dx.doi.org/10.15560/11.2.1582). *Check List*, 11(2):1-6, Article 1582. DOI: dx.doi.org/10.15560/11.2.1582.

## *Under review*
1. **Ramírez-Mejía A F**, Pedro G. Blendinger, Ben A. Woodcock, Reto Schmucki, Lorena Escobar, Richard Daniel Morton, Lorena Vieli, Patrícia Nunes-Silva, Silvia B. Lomáscolo, Carolina Laura Morales, Maureen Murúa, Kayna Agostini, & Natacha P. Chacoff. The step by step of pollination service in blueberry crops. **Second round of revision revisión:** *Journal of Applied Ecology*.

## **In preparation**
1. **Ramírez-Mejía A F**, Chacoff N, Lomáscolo S & Blendinger P. Optimal pollination thresholds to maximize blueberry production.

2. **Ramírez-Mejía A F**, Lomáscolo S, & Blendinger P. Individual and population effectiveness of hummingbirds, wild and managed insect pollinating blueberry crops.

## **Theses**

```{r, eval=FALSE}

tribble(
  ~año, ~titulo, ~tesis,
  2014, "BSc", "Activity, habitat use and species richness of mammals in native forests and eucalyptus plantations in the Colombian Andes",
  2017, "MSc", "Seed dispersion and functional diversity of phyllostomid bats in an anthropogenic landscape: a multi-scale approach",
  2018, "PhD", "Plant-animal interactions in crops and reciprocal effects with the Yungas native forest"
) %>% vitae::brief_entries(with = año,
                           what = tesis,
                           when = glue::glue("{titulo}"))
```

**PhD**. 2018 - 2023 Plant-animal interactions in crops and reciprocal effects with the Yungas native forest. Thesis advisors: [Pedro G. Blendinger](https://scholar.google.com/citations?user=9oyNtX0AAAAJ&hl=en&oi=ao), PhD; independent research CONICET, assistant professor UNT. [Silvia Lomáscolo](https://scholar.google.com/citations?hl=en&user=r9PAo-QAAAAJ), PhD; assistant researcher CONICET.

**MSc**. 2017. Seed dispersion and functional diversity of phyllostomid bats in an anthropogenic landscape: a multi-scale approach. Thesis advisors: [Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=en), PhD; Universidad de los Llanos, Colombia. [J. Nicolás Urbina-Cardona](https://scholar.google.com/citations?user=uMBjaFgAAAAJ&hl=en), PhD; Pontificia Universidad Javeriana, Colombia.

**BSc**. 2014. Activity pattern, habitat use, and mammals richness in native and reforested forests at the Colombian Andes. Thesis advisor: [Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=en), PhD; Universidad Militar Nueva Granada, Cundinamarca, Colombia.



## **Oral Presentations**

```{r P_orales, eval=FALSE}
tribble(
  ~año, ~evento, ~presentacion, ~lugar,
  2014, "II Simposio colombiano de pequeños carnívoros. IV Congreso colombiano de zoología", "Activity and habitat use of soil forage mammals in an Andean forest and a Eucalyptus reforestation", "Cartagena, Colombia",
  2014, "III Simposio regional de biología.", "Species richness, use and traditional knowledge of mammals in the National Natural Park Los Nevados", "Armenia, Colombia"
) %>% 
  detailed_entries(with = evento,
                   what = presentacion,
                   when = año,
                   where = lugar)
```

**2021**. *Blueberry pollination at the NOA, are wild species important?*. Tucumán, Argentina.

**2014**. *Activity and habitat use of soil forage mammals in an Andean forest and a Eucalyptus reforestation*. II Symposium of small carnivores. IV Colombian congres fo zoology. Cartagena, Colombia.

**2014**. *Species richness, use and traditional knowledge of mammals in the National Natural Park Los Nevados*. III Symposium of regional biology. Armenia, Colombia.

# Teaching experience

```{r docente}
tribble(
  ~curso, ~institucion, ~nivel, ~lugar, ~año, ~comentario,
  "Data Clinic", "National University of Tucumán, Faculty of Natural Science and Miguel Lillo Institute", "PhD", "Tucumán, Argentina", 2021, "Biological Science, Agronomy and Biotechnology",
  "Introduction to R programming", "National University of Tucumán, Faculty of Natural Science and Miguel Lillo Institute", "Undergraduate", "Tucumán, Argentina", 2019, "Biological Science"
) %>% 
  detailed_entries(
    with = curso,
    what = institucion,
    where = lugar,
    when = año,
    why = glue::glue("Offered to {comentario} students. Level: {nivel}.")
  )

```

# Graduate courses

```{r cursos_posgrado}

tribble(
  ~curso, ~institucion, ~lugar, ~año, ~duracion, ~nota,
  'Introduction to Bayesian statistics methos in ecology', 'Universidad de Buenos Aires', 'Buenos Aires, Argentina', 2022, '45h', '10/10',
    'Ecosystem services: concepts, tools and perspectives', 'Universidad Nacional de Cuyo', 'Mendoza, Argentina', 2022, '45h', '10/10',
  "Data science with Python", "National University of Southern Patagonia", "Argentina (online)", 2022, "40h", "10/10",
  "Models and data in ecology", "National University of Comahue", "Bariloche, Argenttina (online)", 2021, "40h", "9/10",
  "Statistical tools for addressing gender metrics: a look from graph and systems theory", "National University of Tucumán", "Tucumán, Argentina", 2021, "40h", "100/100",
  "Ecological networks", "University of São Paulo", "São Paulo, Brasil", 2020, "60h", "Excellent",
  "Pollination Ecology", "National University of Comahue", "Bariloche, Argentina", 2019, "60h", "100/100",
  "13° International Pollination Course", "Federal University of Jequitinhonha Valleys", "Minas Gerais, Brasil", 2019, "98h", "100/100",
  "Advanced statistical methods in ecology and evolution", "University of the Uruguay Republic", "Maldonado, Uruguay", 2019, "60h", "100/100",
  "Advanced statistical models using programming language R", "National University of Córdoba", "Córdoba Argentina", 2018, "40h", "100/100"
) %>% 
  detailed_entries(with = curso,
                   what = institucion,
                   where = lugar,
                   when = año,
                   why = glue::glue("Duration: {duracion}. Grade: {nota}"))

```


# Internships

```{r pasantia}
tribble(
  ~pasantia, ~institucion, ~lugar, ~año, ~duracion,
  "Laboratory of Palynology", "National University of Tucumán, Faculty of Natural Science and Miguel Lillo Institute", "Tucumán, Argentina", 2018, "20h"
  
) %>% detailed_entries(with = pasantia,
                       what = institucion,
                       when = año,
                       where = lugar,
                       why = glue::glue("Duration: {duracion}"))

```



# Member of research groups (Colombia)

```{r grupoI}

tribble(
  ~grupo, ~clasificacion, ~institucion, ~vinculacion, ~fechaI, ~fechaF, ~lugar,
  "Ecotonos (Research group in ecology, conservation, taxonomy and systematics)", "C", "University of LLanos", "Active member", "Jan 2017", "Present", "Villavicencio, Colombia",
  "InQuiBio (An integrated research group in chemistry and biology)", "A1", "Military University Nueva granada", "Active member", "Jan 2013", "Dec 2015", "Bogotá, Colombia"
) %>% 
  detailed_entries(with = grupo,
                   what = institucion,
                   why = glue::glue("Classification: {clasificacion}."),
                   where = lugar,
                   when = glue::glue("{fechaI}-{fechaF}"))

```

# Languages
* Spanish.
* English.

# Driver license
* No. 1053795821. Validity: 03-06-2028. Category: B1. Issued: Colombia (03-06-2018).