---
name: Andrés F. Ramírez-Mejía
position: "BSc, MSc, PhD"
address: "Department of Ecology, Zoology and Genetics, Institute of Biology, \\tabularnewline Universidade Federal de Pelotas \\tabularnewline Pelotas (RS), Brasil."
headcolor: "414141"
www: andres-frm.github.io
phone: +55 53 999330101
email: andresfeliper.mejia@gmail.com
github: andres-frm
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
fontsize: 10pt
---



```{r setup, include=FALSE, results='hide', warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pks <- c('vitae', 'tibble', 'tidyverse')

sapply(pks, library, character.only = T)

baretable <- function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL,
                      size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL),
                      longtable = FALSE,
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) |>
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}

```
# Education

```{r educacion, results='asis'}

tribble(
  ~degree, ~Start, ~Start_month, ~End, ~End_month, ~institution, ~place,
  'B.Sc. Biology', 2008 , 'July ', 2014, 'September ', 'University of Caldas (Colombia)', 'Manizales, Colombia',
  'MSc. Conservation and Use of Biodiversity', 2015 , 'August ', 2017, 'August ', 'Pontifical Javeriana University (Colombia)', 'Bogotá, Colombia',
  'Ph.D. Biological Sciences', 2018 , 'August ', 2023, 'August ', 'National University of Tucumán (Argentina)', 'Tucumán, Argentina'
) |> 
  mutate(Date = paste(Start_month, Start, ' -- ', End_month, End, sep = '')) |> 
  detailed_entries(what = degree, 
                   when = Date,
                   where = institution)

```

# Current position

**May 2024 - present**. Postdoctoral researcher with double affiliation: Department of Ecology, Zoology and Genetics, Institute of Biology, Universidade Federal de Pelotas; Department of Zoology & Physiology, University of Wyoming. *Projects*: [Army Ant Followers Project](https://www.tarwaterlab.com/copy-of-panama-plumas-project), and [Hawaii-VINE  Project.](https://www.tarwaterlab.com/hawaii-vine-project)

# Past positions

-   **Jul. 2023 - Apr. 2024.** Postdoctoral researcher at the Institute of Regional Ecology, UNT-CONICET. **Project:** Control systems for pollination service management in blueberry crops.

# Research interests

I am an ecologist with a deep curiosity for understanding how species interactions and functional diversity mediate ecological processes. My background has involved mammals, birds, and pollinators as model systems and the use of quantitative methods and field experiments to address my questions.

\vspace{2mm}

-   Ecological interactions
-   Pollination and frugivory
-   Ecosystem services
-   Community ecology
-   Functional diversity
-   R programming
-   Bayesian statistics

# Technical skills
-   Experimental design and data collection.
-   Causal inference.
-   Data analysis: frequentist and Bayesian statistics (lm, glm, glmm, hierarchical models), Gaussian process models, time series analysis, structural equation modeling, network analysis, fuzzy logic and simulation studies.
-   Programming languages: R (advanced), Python (basic) and Stan (basic).
-   Spatial analysis tools: Google Earth Engine (basic), ArcGis (basic) and R packages: *terra*, *raster*, and *sf* (basic).
-   Other tools: Git and GitHub for version control. RMarkdown and Quarto for report generation.

--------------------------------

# Publication, theses and oral presentations

## Published articles

-   **Ramírez-Mejía A. F.**, Chacoff N., Cavigliasso P., Blendinger P. **(2024)**. How much is enough? Optimizing beehive stocking densities to maximize the production of a pollinator-dependent crop. *Ecological modelling*, vol 498, article number: <https://doi.org/10.1016/j.ecolmodel.2024.110891>.
-   Monasterologo, M, **Ramírez-Mejía A. F.**, et al. **(2024)**. Animal pollination contributes to more than half of Citrus spp. production despite the species and cultivar. *Scientific reports*, vol 14, Article number: 22309.  <https://www.nature.com/articles/s41598-024-73591-6>.
-   Fontanarrosa G., Zarbá L., ... **Ramírez-Mejía A. F.** ... Piquer-Rodríguez M. **(2024)**. Over twenty years of publications in Ecology: Over-contribution of Women reveals a new dimension of gender bias. *PLOS ONE*.  <https://doi.org/10.1371/journal.pone.0307813>
-   **Ramírez-Mejía A F**, Chacoff N, Lomáscolo S, Woodcock B, Schmucki R & Blendinger P. **(2024)**. Optimal pollination thresholds to maximize blueberry production. *Agriculture Ecosystems and Environment* <https://doi.org/10.1016/j.agee.2024.108903>
-   **Ramírez-Mejía A F**, Blendinger P, Woodcock B, Schmucki R, Escobar L, Morton R, Vieli L, Nunes-Silva P, Lomáscolo S, Morales C, Murúa M, Agostini K, & Chacoff N. **(2023)**. Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries. *Journal of Applied Ecology*. DOI: <https://doi.org/10.1111/1365-2664.14553>
-   Nunes-Silva Patrícia, **Ramírez-Mejía Andrés F.**, Blochtein B, Ramos J, Agostini K, Vieli L, Santanna M, Raguse-Quadros M, Maureen M., Chacoff N P, Cavigliasso P, Blendinger P G., Domingos S. **(2023)**. Blueberry: pollination and production in South America. ISBN: 978-65-00-65347-2. DOI: <https://doi.org/10.5281/zenodo.7770381>.
-   **Ramírez-Mejía A F**, Lomáscolo S & Blendinger P. **(2023)** Hummingbirds, honeybees, and wild insect pollinators affect yield and berry quality of blueberries depending on cultivar and farm's spatial context. *Agriculture Ecosystems and Environment*. DOI: <https://doi.org/10.1016/j.agee.2022.108229>
-   Blendinger P G, Rojas T N, **Ramírez-Mejía A F**, Bender I M A, Lomáscolo S, Magro J, Núñez Montellano M G, Ruggera R A, Valoy M & Ordano M. **(2022)** [*Nutrient balance and energy-acquisition effectiveness: do birds adjust their fruit diet to achieve intake targets?*](https://doi.org/10.1111/1365-2435.14164) *Functional Ecology*. DOI: doi.org/10.1111/1365-2435.14164
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2022)**. [*The interplay of spatial scale and landscape transformation moderates the abundance and intraspecific variation in the ecomorphological traits of a phyllostomid bat*](doi:10.1017/S026646742100047X). *Journal of Tropical Ecology*. 38(1), 31-38. DOI: <https://10.1017/S026646742100047X>
-   **Ramírez-Mejía A F**, Echeverry-Galvis M A, & Sánchez F. **(2021)**. [*Activity and habitat use by understory birds in a native Andean forest and a eucalypt plantation*](https://doi.org/10.1676/19-54). *Wilson Journal of Ornithology*. 132(3): 721-729. DOI: doi.org/10.1676/19-54
-   **Ramírez-Mejía A F**, Urbina-Cardona N, & Sánchez F. **(2020)** [*Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis*](https://doi.org/10.1111/btp.12816). *Biotropica*. 52(6): 1168-1182. DOI: <https://doi.org/10.1111/btp.12816>.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2016)**. [*Activity patterns and habitat use of mammals in an Andean forest and a Eucalyptus reforestation in Colombia*](http://doi.org/10.4404/hystrix-27.2-11319). *Hystrix, the Italian Journal of Mammalogy*, 27(2): 104-110. DOI: <https://doi.org/10.4404/hystrix-27.2-11319>.
-   **Ramírez-Mejía A F**, & Sánchez F. **(2015)**. [*Non-volant mammals in a protected area on the Central Andes of Colombia: new records for the Caldas department and the Chinchiná River basin*](http://dx.doi.org/10.15560/11.2.1582). *Check List*, 11(2):1-6, Article 1582. DOI: <https://dx.doi.org/10.15560/11.2.1582>.

## Under review

-   **Ramírez-Mejía A. F.**, Mary De Aquino, Michael Castaño Díaz, Juliana Hinz Wolter, Henry S. Pollock, J. Patrick Kelley, Jeferson Vizentin-Bugoni & Corey E. Tarwater. Biotic and abiotic factors directly and indirectly impact the structure of non-trophic networks across a rainfall gradient. *Journal: Ecology*. **Role: first author**

## Articles in preparation

-   Kimberley Jordan ... **Ramírez-Mejía A. F.**..., Corey E. Tarwater. Testing the space-for-time assumption: precipitation effects on avian body condition across scales. **Role: coauthor, data analysis**
-   Elizabeth Howard ... **Ramírez-Mejía A. F.**..., Corey E. Tarwater. Testing long standing assumptions about army ant swarms: how profitability and dominance alter space use in birds. **Role: coauthor, data analysis**
-   **Ramírez-Mejía A. F.** Drivers of rarity and commonness in Neotropical bats: the role of the landscape, functional traits and intraspecific functional space. **Role: first author**
-   **Ramírez-Mejía A. F.**, A. Carolina Monmany, Roxana Aragón, Carolina Cuezzo, Natalia Ladino, Natalí Villalba, A. Carolina Jozami, Alberto Slanis, Mariano Lucia, Leopoldo Alvarez & Natacha P. Chacoff. Low opportunity cost areas in large-scale monoculture for pollinator conservatio. **Role: first author**


## Code and online datasets

-   **Ramírez-Mejía A. F.**, Chacoff N., Cavigliasso P., & Blendinger P. (2024). How much is enough? Optimizing beehive stocking densities to maximize the production of a pollinator-dependent crop. *Ecological modelling*, vol 498, article number: <https://doi.org/10.1016/j.ecolmodel.2024.110891>. GitHub repository: <https://github.com/andres-frm/postdoc_cropPol>

-   **Ramírez-Mejía, Andrés F**. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [code]. **Journal of Applied Ecology**. Zenodo. <https://doi.org/10.5281/zenodo.10070657>

-   **Ramírez-Mejía, Andrés F**. et al. (2023). Landscape structure and farming management interacts to modulate pollination supply and crop production in blueberries [Dataset]. **Journal of Applied Ecology**. Dryad. <https://doi.org/10.5061/dryad.bg79cnphc>

-   **Ramírez-Mejía, A F**.; Urbina-Cardona, J N; Sánchez, F (2020). Data from: Functional diversity of phyllostomid bats in an urban-rural landscape: a scale-dependent analysis [Dataset]. **Biotropica**. Dryad. <https://doi.org/10.5061/dryad.sn02v6x1p>

## Theses

**PhD**. 2018 - 2023. The step-by-step of pollination service in blueberry crops: patterns and mechanisms. Thesis advisors: [Pedro G. Blendinger](https://scholar.google.com/citations?user=9oyNtX0AAAAJ&hl=en&oi=ao), PhD; independent research CONICET, assistant professor UNT. [Silvia Lomáscolo](https://scholar.google.com/citations?hl=en&user=r9PAo-QAAAAJ), PhD; assistant researcher CONICET.

**MSc**. 2015 - 2017. Seed dispersion and functional diversity of phyllostomid bats in an anthropogenic landscape: a multi-scale approach. Thesis advisors: [Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=en), PhD; Universidad de los Llanos, Colombia. [J. Nicolás Urbina-Cardona](https://scholar.google.com/citations?user=uMBjaFgAAAAJ&hl=en), PhD; Pontificia Universidad Javeriana, Colombia.

**BSc**. 2008 - 2014. Activity patterns, habitat use, and mammals richness in native and reforested forests at the Colombian Andes. Thesis advisor: [Francisco Sánchez](https://scholar.google.com/citations?user=6MC0Yx8AAAAJ&hl=en), PhD; Universidad Militar Nueva Granada, Cundinamarca, Colombia.

## Oral Presentations


**2021**. *Blueberry pollination at the NOA, are wild species important?*. Tucumán, Argentina.

**2014**. *Activity and habitat use of soil forage mammals in an Andean forest and a Eucalyptus reforestation*. II Symposium of small carnivores. IV Colombian congres fo zoology. Cartagena, Colombia.

**2014**. *Species richness, use and traditional knowledge of mammals in the National Natural Park Los Nevados*. III Symposium of regional biology. Armenia, Colombia.

-----------------------------

# Fellowships 

-   **2023**. Postdoctoral fellowship financed by CONICET, Argentina. RESOL‐2023‐1026‐APN‐DIR#CONICET.

-   **2017**. PhD fellowship financed by CONICET, Argentina. N° 4122. Thesis: Plant-animal interaction in blueberry crops (*Vaccinium corymbosum*, Ericaceae) and indirect effect with the Yungas forest.

# Research grants

```{r results='asis'}

tribble(
  ~year, ~proyect, ~funding, ~grant,
  2020, 'Ecosystem services provided by hummingbirds (Trochilidae)','Research grant Aves Argentinas (ARG)', 640,
  2018, 'Ecosystem services provided by hummingbirds (Trochilidae)','Neotropical Ornithological Society (USA)', 1000,
) |> 
  mutate(US = paste(paste('\\$', grant, sep = ''), 'US')) |> 
  select(year, proyect, funding, US) |> 
  baretable()

```

# Distinctions

```{r, results='asis'}

tribble(
  ~year, ~award,
  2017, 'Academic merit award. During MSc degree at Pontifical Javeriana University',
  2017, 'Graduated with honors CUM LAUDE. During MSc degree at Pontifical Javeriana University',
  2017, 'MSc thesis with honorary mention. During MSc degree at Pontifical Javeriana University'
) |> 
  baretable()

```


# Teaching experience

```{r docente, results='asis'}
tribble(
  ~curse, ~institution, ~level, ~year,
  "Data Clinic", "National University of Tucumán", "graduate",  2021, 
  "Introduction to R programming", "National University of Tucumán", "undergraduate", 2019
) |> 
  mutate(
    curse_level = paste(curse, paste('(Level: ', level, ')', sep = ''), sep = ' ')
  ) |> 
  select(year, curse_level, institution) |> 
  baretable()

```

# Graduate courses

```{r cursos_posgrado, results='asis'}

tribble(
  ~year, ~course, ~institution, ~hours, ~country,
  2023, 'Google Earth Engine - Integral', 'REDES Center (CONICET)', 60, 'Argentina',
  2022, 'Introduction to Bayesian statistics methods in ecology', 'University of Buenos Aires', 45, 'Argentina',
  2022, 'Ecosystem services: concepts, tools and perspectives', 'National University of Cuyo', 45, 'Argentina',
  2022, 'Data science with Python', 'National University of Southern Patagonia', 40, 'Argentina',
  2021, 'Models and data in ecology', 'National University of Comahue', 40, 'Argentina',
  2021, 'Statistical tools for addressing gender metrics', 'National University of Tucumán', 40, 'Argentina',
  2020, 'Ecological networks', 'University of São Paulo', 60, 'Brazil',
  2019, 'Pollination Ecology', 'National University of Comahue', 60, 'Argentina',
  2019, '13° International Pollination Course', 'Federal University of Jequitinhonha Valleys', 98, 'Brazil',
  2019, 'Advanced statistical methods in ecology and evolution', 'University of the Uruguay Republic', 60, 'Uruguay',
  2018, 'Advanced statistical models using programming language R', 'National University of Córdoba', 40, 'Argentina'
) |> 
  mutate(h = paste(hours, 'h', sep = '')) |> 
  select(year, course, institution, h, country) |> 
  baretable()
  
```


# Internships

```{r pasantia, results='asis'}

tribble(
  ~pasantia, ~institucion, ~lugar, ~year, ~duracion,
  "Laboratory of Palynology", "National University of Tucumán", "Tucumán, Argentina", 2018, "20h"
  
) |> 
  select(pasantia, institucion, lugar, year) |> 
  baretable()

```



# Member of research groups (Colombia)

```{r grupoI, results='asis'}

tribble(
  ~grupo, ~clasificacion, ~institucion, ~vinculacion, ~fechaI, ~fechaF, ~lugar,
  "Ecotonos", "C", "University of LLanos", "Active member", "Jan 2017", "Present", "Villavicencio, Colombia",
  "InQuiBio", "A1", "Military University Nueva granada", "Past member", "Jan 2013", "Dec 2015", "Bogotá, Colombia"
) |>  
  baretable()

```

# Languages
-   Spanish
-   English
-   Portuguese

# Driver license
* No. 1053795821. Validity: 03-06-2028. Category: B1. Issued: Colombia (03-06-2018).